---
title: "R Notebook"
output: pdf_document
---

# Rstudio API code

# Libraries
```{r}
library(twitteR)
library(ggplot2)
```


# Data Import and Cleaning 

Pulled the api, secret api, access, and secret access codes from twitter in orger to set up the twitter authorization. 
```{r}
api <- "zkHmLKzPFWPc2HfCDbjUU8HP2"
apiSecret <- "JZGwN3tqcQracHJwb2io97wRsLKFO6h1EY8MyEGz3RjGBMwXEx"
access <- "48436651-M7DDZdx7f5BHIIHB4zlH34tMSKxDNLU0XOdD5FKN7"
accessSecret <- "YR2BAv1bXDY9ejt0eaoBtK1y4aeup0Z67XmqtTezIbmF3"

setup_twitter_oauth(api, apiSecret, access, accessSecret)

#Pulled the first 1000 tweets that mention the #rstats. Removed all of those that were retweets and not orginal tweets. Then created a dataframe out of the twitter list. 

tweets <-searchTwitter("#rstats", 1000)
tweets_clean <- strip_retweets(tweets)
tweets_tbl <- twListToDF(tweets_clean)
```

#Analysis 

In this section a correlation test was run between the length of the number of characters in a tweet and the number of retweets. 
```{r}
cor.test(nchar(tweets_tbl$text), tweets_tbl$retweetCount)
```
A plot of the relationship between the length of a tweet and the number of retweets
```{r}
ggplot(tweets_tbl, aes(nchar(tweets_tbl$text), tweets_tbl$retweetCount))+
  geom_point()
```


In this section a correlation test was run between the length of the number of characters in a tweet and the number of favorites. 

```{r}
cor.test(nchar(tweets_tbl$text), tweets_tbl$favoriteCount)
```
#A plot of the relationship between the length of a tweet and the number of favorites

```{r}
ggplot(tweets_tbl, aes(nchar(tweets_tbl$text), tweets_tbl$favoriteCount))+
  geom_point()
```

