---
title: "R Notebook"
author: Dana Tomeh
output: word_document
---

# Rstudio API Code 

# Libraries 

loading the libraries necessary to scrape data from qualtrics and then analyze, and visualize it. 
```{r}
knitr::opts_chunk$set(echo = TRUE)

library(qualtRics)
library(ggplot2)
library(tidyverse)
library(lubridate)
```

# Data Import and Cleaning 
Set up the Qualtrics API, imported all surveys that I have created using the all_surveys() function from the qualtRics package. Mutated the date from character to POSIXct format in order to use for bar chart.
```{r}
qualtrics_api_credentials(api_key = "apikeygoeshere", 
                          base_url = "umn.ca1.qualtrics.com",
                          install = TRUE,
                          overwrite = TRUE)

survey_tbl <- all_surveys() %>%
  mutate(creationDate=ymd_hms(creationDate)) 

```

# Analysis 

# Visualization 

Creating a bar plot of the number of surveys that have been created on a given date using ggplot from the gpplot2 package paired with geom_bar() to indicate the desired bar chart format.
```{r}
ggplot(survey_tbl, aes(creationDate))+ 
  geom_bar() + 
  labs(title = "Number of surveys created on a given date", 
       x= "Date", 
       y= "Number of Surveys Created")
```

